Errata

### 2025-04-15 tex/Manuscript-2.tex
Add appendix table with carbon and nitrogen flux data for study sites

>>>>

\section*{Appendix}

\begin{sidewaystable}[htbp]
  \centering
  \caption[Total content and concentration of carbon and nitrogen for fluxes in sediment and water for the four study sites with and without biocrust cover in percolation and runoff positions]{Total content and concentration of carbon and nitrogen for fluxes in sediment and water for the four study sites (SG: Santa Gracia, QdT: Quebrada de Talca, LC: La Campana, NA: Nahuelbuta) with (+) and without (-) biocrust (BSC) cover in percolation and runoff positions. Carbon and nitrogen values appear as total amounts (g m\textsuperscript{-2} h\textsuperscript{-1}) and as concentrations (\% or ppm).}
  \label{tab:tableA2}
  \begin{tabular}{lllcccccccc}
  \hline
  {\small\textbf{Site}} & 
  {\small\textbf{Biocrust}} & 
  {\small\textbf{Position}} & 
  {\small\textbf{\begin{tabular}[c]{@{}c@{}}Carbon in\\ sediments\\ (g m\textsuperscript{-2} h\textsuperscript{-1})\end{tabular}}} & 
  {\small\textbf{C\textsubscript{T} [\%]}} & 
  {\small\textbf{\begin{tabular}[c]{@{}c@{}}Organic\\ carbon in\\ water\\ (g m\textsuperscript{-2} h\textsuperscript{-1})\end{tabular}}} & 
  {\small\textbf{\begin{tabular}[c]{@{}c@{}}DOC\\ {[ppm]}\end{tabular}}} & 
  {\small\textbf{\begin{tabular}[c]{@{}c@{}}Nitrogen in\\ sediments\\ (g m\textsuperscript{-2} h\textsuperscript{-1})\end{tabular}}} & 
  {\small\textbf{N\textsubscript{T} [\%]}} & 
  {\small\textbf{\begin{tabular}[c]{@{}c@{}}Organic\\ nitrogen in\\ water\\ (g m\textsuperscript{-2} h\textsuperscript{-1})\end{tabular}}} & 
  {\small\textbf{\begin{tabular}[c]{@{}c@{}}DON\\ {[ppm]}\end{tabular}}} \\ 
  \hline
  SG  & BSC+ & percolation & 0.5 ± 0.3  & 0.027 ± 0.010 & 0.7 ± 0.5   & 26 ± 19   & 0.08 ± 0.05  & 0.0041 ± 0.0025 & 0.15 ± 0.13 & 7 ± 12  \\
  SG  & BSC+ & runoff      & 6.4 ± 4.6  & 0.020 ± 0.008 & 0.8 ± 0.5   & 19 ± 12   & 0.47 ± 0.31  & 0.0015 ± 0.0005 & 0.09 ± 0.08 & 2 ± 2   \\
  SG  & BSC- & percolation & 0.4 ± 0.7  & 0.042 ± 0.022 & 0.7 ± 1.1   & 43 ± 31   & 0.05 ± 0.05  & 0.0088 ± 0.0071 & 0.53 ± 1.22 & 28 ± 40 \\
  SG  & BSC- & runoff      & 11.1 ± 4.7 & 0.014 ± 0.004 & 0.5 ± 0.3   & 9 ± 5     & 0.88 ± 0.39  & 0.0011 ± 0.0004 & 0.07 ± 0.06 & 1 ± 1   \\
  QdT & BSC+ & percolation & 0.5 ± 0.3  & 0.045 ± 0.018 & 0.9 ± 0.9   & 27 ± 14   & 0.06 ± 0.03  & 0.0057 ± 0.0023 & 0.10 ± 0.11 & 3 ± 2   \\
  QdT & BSC+ & runoff      & 3.2 ± 1.5  & 0.025 ± 0.009 & 1.6 ± 1.1   & 40 ± 23   & 0.27 ± 0.14  & 0.0021 ± 0.0006 & 0.18 ± 0.12 & 5 ± 3   \\
  QdT & BSC- & percolation & 0.3 ± 0.2  & 0.049 ± 0.021 & 0.3 ± 0.4   & 18 ± 16   & 0.04 ± 0.02  & 0.0072 ± 0.0042 & 0.03 ± 0.04 & 2 ± 3   \\
  QdT & BSC- & runoff      & 12.8 ± 7.3 & 0.021 ± 0.006 & 2.0 ± 1.4   & 56 ± 39   & 1.11 ± 0.68  & 0.0017 ± 0.0004 & 0.34 ± 0.25 & 10 ± 8  \\
  LC  & BSC+ & percolation & 0.8 ± 0.7  & 0.043 ± 0.013 & 1.3 ± 1.1   & 51 ± 29   & 0.14 ± 0.09  & 0.0085 ± 0.0041 & 0.37 ± 0.43 & 13 ± 12 \\
  LC  & BSC+ & runoff      & 3.9 ± 3.5  & 0.049 ± 0.026 & 2.1 ± 1.1   & 47 ± 18   & 0.34 ± 0.30  & 0.0047 ± 0.0024 & 0.40 ± 0.25 & 9 ± 4   \\
  LC  & BSC- & percolation & 0.5 ± 0.3  & 0.051 ± 0.029 & 0.8 ± 0.7   & 34 ± 18   & 0.09 ± 0.07  & 0.0082 ± 0.0030 & 0.21 ± 0.31 & 8 ± 6   \\
  LC  & BSC- & runoff      & 23.1 ± 13.7& 0.063 ± 0.026 & 0.8 ± 0.6   & 22 ± 6    & 1.44 ± 0.83  & 0.0038 ± 0.0011 & 0.27 ± 0.25 & 7 ± 3   \\
  NA  & BSC+ & percolation & 2.3 ± 2.2  & 0.095 ± 0.060 & 0.6 ± 0.7   & 7 ± 7     & 0.13 ± 0.10  & 0.0062 ± 0.0034 & 0.03 ± 0.05 & 0 ± 1   \\
  NA  & BSC+ & runoff      & 2.0 ± 2.2  & 0.115 ± 0.047 & 0.1 ± 0.2   & 4 ± 5     & 0.12 ± 0.18  & 0.0059 ± 0.0015 & 0.00 ± 0.01 & 0 ± 1   \\
  NA  & BSC- & percolation & 2.3 ± 1.3  & 0.114 ± 0.034 & 0.3 ± 0.3   & 8 ± 7     & 0.12 ± 0.06  & 0.0065 ± 0.0014 & 0.05 ± 0.06 & 2 ± 5   \\
  NA  & BSC- & runoff      & 8.2 ± 6.5  & 0.196 ± 0.067 & 0.3 ± 0.4   & 5 ± 5     & 0.32 ± 0.25  & 0.0079 ± 0.0024 & 0.04 ± 0.06 & 1 ± 1   \\
  \hline
  \end{tabular}
  \end{sidewaystable}
